---
title: "CapstoneProjectFinalProject"
author: "GaryFH"
date: "October 25, 2017"
output: html_document
---

##Setup work environment

```{r warning=F,message=F}
library(tm)
library(stringi)
library(wordcloud)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(knitr)
library(RWeka)
library(futile.logger)
library(SnowballC)
library(doParallel)
library(textcat)
library(stringr)

options(digits = 2)
```

##Load "en_US.blogs.txt", "en_US.news.txt", "en_US.twitter.txt" into the R work environment and check time

```{r warning=F,message=F}
getdata_start=proc.time()
blog <- readLines(file("en_US.blogs.txt"), skipNul = TRUE)
twit <- readLines(file("en_US.twitter.txt"), skipNul = TRUE)
news <- readLines(file("en_US.news.txt"), skipNul = TRUE)
badwords<-readLines(file( "https://raw.githubusercontent.com/shutterstock/List-of-Dirty-Naughty-Obscene-and-Otherwise-Bad-Words/master/en"),skipNul = TRUE)
getdata_stop=proc.time()
getdata_time=getdata_stop-getdata_start
getdata_time
totaldata<-c(blog,twit,news)

```

#make a function to clean data   x=datasource

```{r warning=F,message=F}

GFtextcleaner<-function(x) {
              
      GFtext <- Corpus(VectorSource((x)))
      GFtext <- tm_map(GFtext, PlainTextDocument)
      GFtext <- tm_map(GFtext, stripWhitespace)
      GFtext<- tm_map(GFtext, content_transformer(tolower))
      GFtext <- tm_map(GFtext, removePunctuation)
      GFtext <- tm_map(GFtext, removeNumbers)
      GFtext <- tm_map(GFtext, removeWords, badwords)
      GFtext <- tm_map(GFtext, stripWhitespace)
     
#      GFtext <- tm_map(GFtext, removeWords, c("a","and","the","an"))
#      GFtext <- tm_map(GFtext,removeWords,stopwords(kind="en"))
      
      data.frame(sapply(GFtext,as.character),stringsAsFactors = FALSE) 
      
}


```


#Make a function with Weka to creat a corpus as needed  x=datasource,y=number of "grams"

```{r warning=F,message=F}
GFcorpuscreate<-function (x,y){
      arrange(tbl_df(data.frame(table(NGramTokenizer(x,Weka_control(min=y, max=y))))),desc(Freq))
}



```


#Make training and test datasets 

```{r warning=F,message=F}
set.seed(234)

GFtrain<-sample(totaldata,40000)
#GFtest<-sample(totaldata,1000)


```



#Create Function to make n-grams  x=datasource,y=number of "grams"

```{r warning=F,message=F}
GFgrammaker<-function(x,y) {
        GFcorpuscreate(GFtextcleaner(x),y)
        
}


```




#create and save n-grams (2, 3 & 4grams)

```{r warning=F,message=F}

#GFgram1<-GFgrammaker(GFtrain,1)
#GFgram1$pred<-"n/a"
#rowname1<-c(1:nrow(GFgram1))
#saveRDS(GFgram1, file="GFgram1.rds")

GFgram2<-GFgrammaker(GFtrain,2)
rowname2<-c(1:nrow(GFgram2))
GFgram2$word1 <-word(GFgram2$Var1,1)
GFgram2$word2 <-word(GFgram2$Var1,2)
saveRDS(GFgram2, file="GFgram2.rds")

GFgram3<-GFgrammaker(GFtrain,3)
rowname3<-c(1:nrow(GFgram3))
GFgram3$word1 <-word(GFgram3$Var1,1)
GFgram3$word2 <-word(GFgram3$Var1,2)
GFgram3$word3 <-word(GFgram3$Var1,3)
saveRDS(GFgram3, file="GFgram3.rds")

GFgram4<-GFgrammaker(GFtrain,4)
GFgram4$word1 <-word(GFgram4$Var1,1)
GFgram4$word2 <-word(GFgram4$Var1,2)
GFgram4$word3 <-word(GFgram4$Var1,3)
GFgram4$word4 <-word(GFgram4$Var1,4)
saveRDS(GFgram4, file="GFgram4.rds")


#GFgram5<-GFgrammaker(GFtrain,5)

#head(GFgram1)
head(GFgram2)
head(GFgram3)
head(GFgram4)
```




